Factors affecting health sector expenditure in OECD countries

### 2025-01-31 products/manuscript/Manuscript.qmd
updates to page title

---
title: "Prasanga Paudel- Data Analysis Project"
author: ""
format:
  html:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

* First Autor$^{1,2,*}$ (ORCID: 0000-0000-1234-5678) 
* Second Author$^{3, *}$
* Third Autor$^{3, \dagger}$
* Last Author$^{1, 2, \land}$

@@

1. College of Public Health, University of Georgia, Athens, GA, USA.
2. Another Affiliation, Athens, GA, USA.
3. Yet another Affiliation.

@@

## General Background Information
_We will try to analyze the most influential factors affecting the expenditure in health sector by different countries. The predictor variables will include factors ranging from education, mortality, population distribution among rural and urban spaces, and so on. We would use multiple regression analysis with health sector expenditure as dependent variable and the variable of interests as predictors._

_We are using data from OECD members for analysis, and there have already been some research which have focused on GDP as predictor for health sector expenditure. Some research have also focused on the relation between life expectancy and health expenditure. However, these research were based on fixed effect and random effect models. In our analysis we will try to follow OLS based multiple regression model._

@@

## Objective of the research
_The main objective of this research is to:_

>>>>

---
title: "Factors affecting health sector expenditure in OECD countries"
author: "Prasanga Paudel"
format:
  html:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

* Prasanga Paudel$^{1,2,*}$ (ORCID: 0000-0000-1234-5678) 
* Second Author$^{3, *}$
* Third Autor$^{3, \dagger}$
* Last Author$^{1, 2, \land}$

@@

1. College of Agricultural and Environmental Science, University of Georgia, Athens, GA, USA.
2. Another Affiliation, Athens, GA, USA.
3. Yet another Affiliation.

@@

## General Background Information
_We will try to analyze the most influential factors affecting the expenditure in health sector by different countries. The predictor variables will include factors ranging from education, mortality, population distribution among rural and urban spaces, and so on. We would use multiple regression analysis with health sector expenditure as dependent variable and the variable of interests as predictors for this panel data._

_We are using data from OECD members for analysis, and there have already been some research which have focused on GDP as predictor for health sector expenditure. Some research have also focused on the relation between life expectancy and health expenditure. However, these research were based on fixed effect and random effect models. In our analysis we will try to follow OLS multiple regression model._

@@

## Objective of the research

The expenditure in health sector is one of the important factor that helps in determining the efficiency of health sector. We can relate the expenditure with different national development indicators and hope to find important connections between them. This will help government to make specific interventions through their policy to enhance their health sector. We can also find out how countries are currently operating and which factor has helped or negatively affected their health sector.

_The main objective of this research is to:_
